\textbf{Preprinting Microbiology}

### 2017-02-07 submission/Schloss_PrePrints_mBio_2017.Rmd
Editing

inline_hook <- function(x){
	print(x)
	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=2, nsmall=2, scientific=FALSE))
		}

@@

***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, we downloaded the *bioRxiv* on December 31, 2016. We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*. Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories. To counter this limitation, we developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, or *pathogen*. We identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that we considered microbiology-affiliated. These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories. As the total number of preprints has grown exponentially since the creation of *biorxiv*, submission of microbiology-affiliated preprints has largely followed this growth (**Figure 1A**).

Although preprints are still relatively new, the collection of microbiology-affiliated preprints indicates widespread experimentation with the format and considerable geographic diversity. Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r 100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r 100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts)`% have posted 3 or more preprints. Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%). As the preprint format matures, it will be interesting to see whether the fraction of authors that post multiple preprints increases and whether the geographic diversity amongst those authors is maintained.

@@

Measuring the impact and significance of scientific research is notoriously difficult. Using several metrics we sought to quantify the effect that microbiology-affiliated preprints have had on the work of others. Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively. These values represent two aspects of posting a preprint. First, they reflect the number of times people were able to access science before it was published. Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall. To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint (**Figure 1B**). The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, mainstream media, Wikipedia, policy documents, and other sources [@Altmetric]. A higher score indicates that a preprint received more attention. Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`). For comparison, the median Altmetric Attention Score for articles published in *mBio* published since November 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`). Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *biorxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`. A more traditional and controversial metric of impact has been the number of citations an article receives. We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints. To allow for a comparison to traditional journals, we considered the citations for preprints published in 2014 and 2015 as aggregated by Web of Science (**Figure 1C**). Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`). For comparison, for the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`). Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community

>>>>

inline_hook <- function(x){
	print(x)
	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=1, nsmall=1, scientific=FALSE))
		}

@@

***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, we downloaded the *bioRxiv* on December 31, 2016. We chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,650 available at *PeerJ Preprint*. Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories. To counter this limitation, we developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, or *pathogen*. We identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that we considered microbiology-affiliated. These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.

As the total number of preprints has grown exponentially since the creation of *bioRxiv*, submission of microbiology-affiliated preprints has largely followed this growth (**Figure 1A**). Although preprints are still relatively new, the collection of microbiology-affiliated preprints indicates widespread experimentation with the format and considerable geographic diversity. Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r round(100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts), 1)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r round(100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts), 1)`% have posted 3 or more preprints. Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r round(micro_aff_countries_percent[1], 1)`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r round(micro_aff_countries_percent[2], 1)`%), and `r micro_aff_countries_names[3]` (`r round(micro_aff_countries_percent[3], 1)`%). As the preprint format matures, it will be interesting to see whether the fraction of authors that post multiple preprints increases and whether the geographic diversity amongst those authors is maintained.

@@

Measuring the impact and significance of scientific research is notoriously difficult. Using several metrics we sought to quantify the effect that microbiology-affiliated preprints have had on the work of others. Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively. These values represent two aspects of posting a preprint. First, they reflect the number of times people were able to access science before it was published. Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall. To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint (**Figure 1B**). The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, traditional media, Wikipedia, policy documents, and other sources [@Altmetric]. A higher score indicates that a preprint received more attention. Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). For comparison, the median Altmetric Attention Score for articles published in *mBio* published since 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(round(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *biorxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`. A more traditional and controversial metric of impact has been the number of citations an article receives. We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints. To allow for a comparison to traditional journals, we considered the citations for preprints published in 2014 and 2015 as aggregated by Web of Science (**Figure 1C**). Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`). For comparison, for the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`). Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community

### 2017-02-07 submission/Schloss_PrePrints_mBio_2017.tex
Editing

\textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
analyze the use of preprints, we downloaded the \emph{bioRxiv} on
December 31, 2016. We chose to analyze the use of \emph{bioRxiv}
preprints because these preprints are amenable for submission to ASM
journals and there were 7,434 preprints compared to the 2,650 available
at \emph{PeerJ Preprint}. Among the 7,434 preprints on bioRxiv, 329 were
assigned by the authors into the Microbiology category. One limitation
of the \emph{bioRxiv} interface is the inability to assign manuscripts
to multiple categories or to tag the content of the preprint. For
example, this manuscript could be assigned to either the Microbiology or
the Scientific Communication and Education categories. To counter this
limitation, we developed a more permissive approach that classified
preprints as being microbiology-affiliated if their title or abstract
had words containing \emph{yeast}, \emph{fung}, \emph{viral},
\emph{virus}, \emph{archaea}, \emph{bacteri}, \emph{microb},
\emph{microorganism}, or \emph{pathogen}. We identified 1,228 additional
manuscripts that we considered microbiology-affiliated. These
microbiology-affiliated preprints were primarily assigned to the
Evolutionary Biology (N=221), Genomics (N=184), or Bioinformatics
(N=182) categories. As the total number of preprints has grown
exponentially since the creation of \emph{biorxiv}, submission of
microbiology-affiliated preprints has largely followed this growth
(\textbf{Figure 1A}).

Although preprints are still relatively new, the collection of
microbiology-affiliated preprints indicates widespread experimentation
with the format and considerable geographic diversity. Reflecting the
still relatively novelty of preprints, 1,132 (86.15\%) corresponding
authors who submitted a microbiology-affiliated manuscript (N=1,314
total) have posted a single preprint and 3.58\% have posted 3 or more
preprints. Corresponding authors that have posted
microbiology-affiliated preprints are from 60 countries and are
primarily affiliated with institutions in the United States (50.80\% of
microbiology-affiliated preprints), United Kingdom (11.95\%), and
Germany (4.17\%). As the preprint format matures, it will be interesting
to see whether the fraction of authors that post multiple preprints
increases and whether the geographic diversity amongst those authors is
maintained.

As stated above, preprints offer researchers the opportunity to improve
the quality of their work by adding a more formal and public step to the
scientific process. Among the microbiology-affiliated manuscripts, 146
(9.32\%) had been commented on at least once and only 35 (2.23\%) more
than three times using the \emph{bioRxiv}-hosted commenting feature.
Although the hosted commenting is only one mechanism for peer review,
this result was somewhat disturbing since the preprint model implicitly
depends on people's willingness to offer others feedback. Regardless,
authors do appear to be incorporating feedback from colleagues or
editorial insights from journals as 404 (25.80\%) of preprints were
revised at least once. Among the preprints posted prior to January 1,
2016, 31.61\% of the Microbiology category preprints, 35.12\% of the
microbiology-affiliated preprints, and 33.79\% of all preprints have
been published. As noted above, not all authors submit their preprints
to journals. This would indicate that the ``acceptance rates'' are
actually higher. Regardless, considering that these acceptance rates are
higher than many peer-reviewed journals (e.g.~approximately 20\% at ASM
Journals), these results dispel the critique that preprints represent
overly preliminary research.

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics we sought to quantify the
effect that microbiology-affiliated preprints have had on the work of
others. Using the download statistics associated with each preprint, we
found that the median number of times an abstract or PDF had been
accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to 568),
respectively. These values represent two aspects of posting a preprint.
First, they reflect the number of times people were able to access
science before it was published. Second, they reflect the number of
times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the public, we obtained the Altmetric
Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
Attention Score measures the number of times a preprint or paper is
mentioned in social media, mainstream media, Wikipedia, policy
documents, and other sources (33). A higher score indicates that a
preprint received more attention. Microbiology-affiliated preprints have
had a median Altmetric Attention Score of 7.28 (IQR: 3.25 to 16.3495)
and those of all preprints hosted at \emph{bioRxiv} have had a median
score of 7.05 (IQR: 3 to 15.556). For comparison, the median Altmetric
Attention Score for articles published in \emph{mBio} published since
November 2013 was 4.45 (IQR: 1.25 to 13.604). Of all scholarship tracked
by Altmetric, the median Altmetric Attention Score for preprints posted
at \emph{biorxiv} ranks at the 86 percentile (IQR: 66 to 94. A more
traditional and controversial metric of impact has been the number of
citations an article receives. We obtained the number of citations for
the published versions of manuscripts that were initially posted as
preprints. To allow for a comparison to traditional journals, we
considered the citations for preprints published in 2014 and 2015 as
aggregated by Web of Science (\textbf{Figure 1C}). Among the preprints
that were published and could be found in the Web of Science database,
the median number of citations was 6.50 (IQR: 2-14; mean: 13.60). For
comparison, for the papers published in \emph{mBio} in 2014 and 2015,
the median number of citations was 5 (IQR: 2-9; mean: 6.73). Although it
is impossible to quantify the quality or impact of research with
individual metrics, it is clear that preprints and the publications that
result from them are broadly accepted by the microbiology community

>>>>

\textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
analyze the use of preprints, we downloaded the \emph{bioRxiv} on
December 31, 2016. We chose to analyze \emph{bioRxiv} preprints because
these preprints are amenable for submission to ASM journals and there
were 7,434 \emph{bioRxiv} preprints compared to the 2,650 available at
\emph{PeerJ Preprint}. Among the 7,434 preprints on bioRxiv, 329 were
assigned by the authors into the Microbiology category. One limitation
of the \emph{bioRxiv} interface is the inability to assign manuscripts
to multiple categories or to tag the content of the preprint. For
example, this manuscript could be assigned to either the Microbiology or
the Scientific Communication and Education categories. To counter this
limitation, we developed a more permissive approach that classified
preprints as being microbiology-affiliated if their title or abstract
had words containing \emph{yeast}, \emph{fung}, \emph{viral},
\emph{virus}, \emph{archaea}, \emph{bacteri}, \emph{microb},
\emph{microorganism}, or \emph{pathogen}. We identified 1,228 additional
manuscripts that we considered microbiology-affiliated. These
microbiology-affiliated preprints were primarily assigned to the
Evolutionary Biology (N=221), Genomics (N=184), or Bioinformatics
(N=182) categories.

As the total number of preprints has grown exponentially since the
creation of \emph{bioRxiv}, submission of microbiology-affiliated
preprints has largely followed this growth (\textbf{Figure 1A}).
Although preprints are still relatively new, the collection of
microbiology-affiliated preprints indicates widespread experimentation
with the format and considerable geographic diversity. Reflecting the
still relatively novelty of preprints, 1,132 (86.1\%) corresponding
authors who submitted a microbiology-affiliated manuscript (N=1,314
total) have posted a single preprint and 3.6\% have posted 3 or more
preprints. Corresponding authors that have posted
microbiology-affiliated preprints are from 60 countries and are
primarily affiliated with institutions in the United States (50.8\% of
microbiology-affiliated preprints), United Kingdom (11.9\%), and Germany
(4.2\%). As the preprint format matures, it will be interesting to see
whether the fraction of authors that post multiple preprints increases
and whether the geographic diversity amongst those authors is
maintained.

As stated above, preprints offer researchers the opportunity to improve
the quality of their work by adding a more formal and public step to the
scientific process. Among the microbiology-affiliated manuscripts, 146
(9.3\%) had been commented on at least once and only 35 (2.2\%) more
than three times using the \emph{bioRxiv}-hosted commenting feature.
Although the hosted commenting is only one mechanism for peer review,
this result was somewhat disturbing since the preprint model implicitly
depends on people's willingness to offer others feedback. Regardless,
authors do appear to be incorporating feedback from colleagues or
editorial insights from journals as 404 (25.8\%) of preprints were
revised at least once. Among the preprints posted prior to January 1,
2016, 31.6\% of the Microbiology category preprints, 35.1\% of the
microbiology-affiliated preprints, and 33.8\% of all preprints have been
published. As noted above, not all authors submit their preprints to
journals. This would indicate that the ``acceptance rates'' are actually
higher. Regardless, considering that these acceptance rates are higher
than many peer-reviewed journals (e.g.~approximately 20\% at ASM
Journals), these results dispel the critique that preprints represent
overly preliminary research.

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics we sought to quantify the
effect that microbiology-affiliated preprints have had on the work of
others. Using the download statistics associated with each preprint, we
found that the median number of times an abstract or PDF had been
accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to 568),
respectively. These values represent two aspects of posting a preprint.
First, they reflect the number of times people were able to access
science before it was published. Second, they reflect the number of
times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the public, we obtained the Altmetric
Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
Attention Score measures the number of times a preprint or paper is
mentioned in social media, traditional media, Wikipedia, policy
documents, and other sources (33). A higher score indicates that a
preprint received more attention. Microbiology-affiliated preprints have
had a median Altmetric Attention Score of 7.3 (IQR: 3.2 to 16.3) and
those of all preprints hosted at \emph{bioRxiv} have had a median score
of 7.0 (IQR: 3 to 15.6). For comparison, the median Altmetric Attention
Score for articles published in \emph{mBio} published since 2013 was 4.5
(IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
Altmetric Attention Score for preprints posted at \emph{biorxiv} ranks
at the 86 percentile (IQR: 66 to 94. A more traditional and
controversial metric of impact has been the number of citations an
article receives. We obtained the number of citations for the published
versions of manuscripts that were initially posted as preprints. To
allow for a comparison to traditional journals, we considered the
citations for preprints published in 2014 and 2015 as aggregated by Web
of Science (\textbf{Figure 1C}). Among the preprints that were published
and could be found in the Web of Science database, the median number of
citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, for the
papers published in \emph{mBio} in 2014 and 2015, the median number of
citations was 5 (IQR: 2-9; mean: 6.7). Although it is impossible to
quantify the quality or impact of research with individual metrics, it
is clear that preprints and the publications that result from them are
broadly accepted by the microbiology community
